Joint analysis of read count data

### 2020-09-04 combined_analysis/combine_all_data.Rmd
Fix Dx

```{r plots.marginal}
# Disease
tab = topTable(fit_marginal, "Scz", number=Inf) %>% getGeneSymbol
fig1 = plotVolcano( tab, rownames(tab)[1:20] ) + ggtitle("SCZ")

tab = topTable(fit_marginal, "BP", number=Inf)
fig2 = plotVolcano( tab, rownames(tab)[1:20] ) + ggtitle("BP")

@@

# Sex
tab = topTable(fit_marginal, "Reported_GenderMale", number=Inf) %>% getGeneSymbol

fig3 = plotVolcano( tab ) + ggtitle("Sex")
fig4 = plotVolcano( tab[tab$Chrom %in% 1:22,] ) + ggtitle("Sex")

>>>>

```{r plots.marginal}
# Disease
tab = topTable(fit_marginal, "Scz", number=Inf) %>% getGeneSymbol
fig1 = plotVolcano( tab, tab$Symbol[1:20] ) + ggtitle("SCZ")

tab = topTable(fit_marginal, "BP", number=Inf)
fig2 = plotVolcano( tab, tab$Symbol[1:20] ) + ggtitle("BP")

@@

# Sex
tab = topTable(fit_marginal, "Reported_GenderMale", number=Inf) %>% getGeneSymbol
fig3 = plotVolcano( tab, tab$Symbol[1:20] ) + ggtitle("Sex")

tab2 = tab[tab$Chrom %in% 1:22,]
fig4 = plotVolcano( tab2, tab2$Symbol[1:20]) + ggtitle("Sex")
